From heartbeat to data -- Using wearable fitness trackers as an affordable approach to assess teacher stress

### 2024-09-26 02_paper/02_study/01_fitbit paper/Submission/FitBit_submission.tex
paar fehler behoben

  \title{From heartbeat to data -- Using wearable fitness trackers as an
affordable approach to assess teacher stress}
    \author[Leipzig University]{Mandy Klatt%
  \corref{cor1}%
  \fnref{1}}
   \ead{mandy.klatt@uni-leipzig.de} 
    \author[University of Greifswald]{Peer Keßler%
  %
  \fnref{2}}
   \ead{peer.kessler@uni-greifswald.de.com} 
    \author[Leipzig University, Max Planck Institute for Evolutionary
Anthropology]{Gregor Kachel%
  %
  \fnref{1}}
   \ead{gregor@example.com} 
    \author[Leipzig University]{Christin Lotz%
  %
  \fnref{1}}
   \ead{christin.lotz@uni-leipzig.de} 
    \author[Leipzig University]{Anne Deiglmayr%
  %
  \fnref{3}}
   \ead{anne.deiglmayr@uni-leipzig.de} 
      \affiliation[Leipzig University]{
    organization={Empirische Schul- und
Unterrichtsforschung},addressline={Marschnerstr.
29},city={Leipzig},postcode={4109},state={Sachsen},country={Germany},}
    \affiliation[Max Planck Institute for Evolutionary Anthropology]{
    organization={Department},addressline={Deutscher Pl.
6},city={Leipzig},postcode={4103},state={Sachsen},country={Germany},}
    \affiliation[University of Greifswald]{
    organization={Institute of Psychology},addressline={Robert-Blum-Str.
13},city={Greifswald},postcode={17489},state={Mecklenburg-Vorpommern},}
    \cortext[cor1]{Corresponding author}
    \fntext[1]{Conceptualization,Writing - Original Draft
Preparation,Writing - Review \& Editing}
    \fntext[2]{Writing - Original Draft Preparation,Writing - Review \&
Editing}
    \fntext[3]{Supervision}

@@

Each participant came to the lab for a period of approximately two hours
in total, and each participant underwent the same phases (see Figure
\ref{fig.2}): In the \emph{pre-teaching phase}, the experimenter
welcomed the participants and helped them put on the fitness tracker.
This was followed by a warm-up session to familiarize the participants
with the laboratory setting and the class. This phase took about 10-15
minutes and participants spent this time mostly standing or slowly
walking around. During the \emph{teaching phase}, the participants held
their self-prepared micro-teaching unit to a class of three trained
actors who performed nine, potentially disruptive, classroom events
(e.g., chatting with a neighbor, heckling, looking at the phone; see
Table \#\# in the supplementary material for an overview and
categorization of all events; and Figure \ref{fig.a2} in the
supplementary material for a depiction of the laboratory setting of the
micro-teaching unit). The topic and class level of the teaching unit
could be freely chosen by the teachers with the only requirement that
the unit had to be an introductory lesson, and had to consist of
supervised individual work and / or frontal teaching. The micro-teaching
unit lasted about 15-20 minutes. Participants spent this time mostly
standing or slowly walking around. While teaching, participants wore
eye-tracking glasses, and their lesson was video-recorded. After having
completed the micro-teaching unit, in the \emph{post-teaching phase},
participants filled in questionnaires for approximately 10-15 minutes: a
brief computer-based survey of sociodemographic

@@

Since we aimed to keep measurement intervals comparable between study
phases, we aggregated HR over a representative 10-minute interval within
each phase (cf.~Fig. 2). Previous research has indicated that 10-minute
intervals are a useful duration for analyzing PPG data
\citep{lu2008can}. The intervals were selected based on the following
rules: The \emph{pre-teaching interval} (\(I_1\)) comprised the first 10
minutes after the fitness tracker had been put on. The \emph{teaching
interval} (\(I_2\)) started two minutes after the lesson had started.
This interval was of the highest relevance to our study. We explicitly
chose an early 10-minute interval within the teaching phase, as previous
studies revealed that the beginning of a lesson is most demanding and
potentially stressful with regards to teacher-student interaction
\citep{donker2018, claessens2017positive}. The \emph{post-teaching
interval} (\(I_3\)) started immediately after the end of the teaching
unit. The \emph{interview interval} (\(I_4\)) was defined as the mid-10
minutes between the end of the teaching unit and the time point when the
fitness tracker was taken off. All participants were being interviewed
during this interval. The end interval (I5) comprised the last 10
minutes before the fitness tracker was taken off.

@@

To enable visual inspection of HR trends, we displayed smoothed teacher
HR over the course of the recording\footnote{The curve was smoothed
  using the geom\_smooth() function from the ggplot2 package in R
  \citep{ggplot2} based on the smoothing method LOESS (Locally Estimated
  Scatterplot Smoothing). This method fits a polynomial surface
  determined by one or more numerical predictors, using local fitting.}.
We visually compared unstandardized and standardized HR trends over the
two-hour recording period\footnote{Note that the study exceeded the
  planned duration of two hours for a few participants. To avoid
  distortions when mapping the HR over the course of the study (see Fig.
  3), the endpoint was set at two hours for all participants, even
  though data from later time points was used in the \emph{end interval}
  for a few participants.}. For all further analyses, we used
standardized rather than unstandardized HR values.

@@

Addressing our second research goal, we ran linear regression analysis
with teaching experience and subjective appraisals as predictors. To
test Hypothesis 2a, we examined the effect of teaching experience on
participants' HR levels (i.e., mean standardized HR) for each of the
five intervals, using linear regression models with teaching experience
as the sole predictor. To test Hypotheses 2b and 2c, we separately
augmented the model by either teachers' disruption appraisal (Hypothesis
2b) or confidence appraisal (Hypothesis 2c) as predictors, while
controlling for teaching experience. To test Hypothesis 2d, we examined
the effects of all three predictors in one regression model.
Furthermore, we repeated these steps to explore the effects of teaching
experience and subjective appraisals on \emph{changes} in teachers' HR
(i.e., mean slopes). Please note: HR levels and changes were not
regressed on the disruption and confidence appraisals in the
\emph{pre-teaching interval} (\(I_1\)), because the appraised classroom
events had not yet taken place in that phase.

@@

Table 3 shows the raw correlations among mean standardized HR/mean
slopes (see Table 2 for means and standard deviations), teaching
experience (\(M = 5.64\), \(SD = 9.46\)), disruption appraisal
(\(M = 5.19\), \(SD = 2.87\)), and confidence appraisal (\(M = 7.81\),
\(SD = 1.97\)). With a few notable exceptions, correlations with HR
measures were mostly very small and statistically non-significant (Table
3). Correlations between teaching experience and appraisals (not shown
in Table 3) were substantial: more experienced teachers gave lower
disruption appraisals (\(r = -.36\)), and higher confidence appraisals
(\(r = .44\)). Moreover, the two appraisal variables were negatively
correlated (\(r = -.37\)).

Table 4 shows the results of the regression analyses. Teaching
experience significantly predicted mean standardized HR only in the
\emph{interview interval} (Table 4, Interview interval, Model 1),
indicating a higher mean standardized HR for teachers with more teaching
experience. This relationship is, in fact, in the opposite direction as
predicted by Hypothesis 2a. Neither adding disruption appraisal
(\textbf{Hypothesis 2b}) nor adding confidence appraisal
(\textbf{Hypothesis 2c}) increased the amount of explained variance to a
statistically significant extent.

When considering the effects of the three predictors in concert
(\textbf{Hypothesis 2d}), mean standardized HR was significantly
predicted only by disruption appraisal, and only in the
\emph{post-teaching interval} (Table 4, Post-teaching interval, Model
4), indicating a higher mean standardized HR for teachers who felt more
disrupted by the classroom events, when controlling for the other
variables.

@@

Building on the model of teacher stress \citep[see Fig.
2]{kyriacou1978}, we had hypothesized that more experienced teachers,
with better classroom management skills at their disposal, experience
less physiological stress when dealing with classroom disruptions.
Contrary to our expectations, we found no buffering effect of teaching
experience on teachers' HR, i.e., more experienced teachers did not show
lower mean standardized HR during the stressful teaching phase than less
experienced teachers. Rather, at least descriptively, we observed the
opposite trend. There are several possible explanations for this
finding. First, teaching experience is inherently confounded with age
(the two variables correlated at \(r = .94\) in our sample), and age has
been shown to affect indicators of cardiovascular reactivity in various
ways \citep{uchino2010older}. However, to avoid this kind of confounding
influence, we had used not raw BPM but rather standardized mean HR for
all our analyses, thus controlling at least for inter-individual
differences in mean HR. Second, as research on teacher
professionalization has repeatedly shown, professional experience is not
a guarantee for higher professional knowledge and skills
\citep{kirschner2016professionswissen}. Rather, honing skills from
professional experience necessitates a deliberate practice of choosing
to improve, learning through experience, and integrating new knowledge
into future performances \citep{dunn1999deliberate}. Thus, rather than
professional experience alone, more direct assessments of classroom
management skills, such as objective behavior-based tests, would be a
better indicator of expertise that future studies could explore.
Finally, and most importantly, the highly controlled teaching situation
that we created in the lab might not have provided sufficient
resemblance to the expert teachers' working conditions to let them
effectively use their coping resources. In other words, since the
situation was unfamiliar to both experienced and unexperienced teachers,
their stress levels might have been more similar than they would have
been in a more authentic classroom setting.

While we did not find a buffering effect of teaching experience on mean
HR during teaching, we did, however, find a less steep HR increase in
more experienced, compared to less experienced teachers during the
pre-teaching phase (\(\beta = -.27\)), i.e., in preparation for the
micro-teaching unit. This finding supports the idea that, even though
teaching experience guarantees neither superior expertise nor stress
resistance, the habits and routines formed by experienced teachers may
at least lead to lower arousal levels (e.g., experienced as feeling less
nervous and tense) when they anticipate potentially stressful teaching
situations.

An interesting observation beyond our hypotheses was that teaching
experience was predictive of HR differences, not during teaching, but in
the interview phase: compared to less experienced teachers, more
experienced teachers showed a higher mean standardized HR
(\(\beta = .24\)) and, thus, probably experienced higher levels of
physiological stress during the SRI. One possible explanation for this
finding could again be the higher age of the more experienced teachers,
along with slower recovery from stress in older teachers. For instance,
\citet{ritvanen2006responses} observed that, compared to their younger
colleagues, older teachers did not experience a decrease in their HR
during periods of low stress levels, from which they concluded that
recovery from stress was insufficient in the older teachers
\citep{ritvanen2006responses}. Alternatively, the finding could also be
attributed to the fact that less experienced teachers, due to their
ongoing or only recently concluded training, may have been more
accustomed to reflecting on their work and receiving feedback as was the
case during the SRI, whereas, these activities were less routine and
possibly more face-threatening for experienced teachers. Therefore, it
is possible that more experienced teachers found the interview itself to
be more stressful and therefore showed a higher mean standardized HR
during this phase.

With regards to the predictive power of teachers' subjective appraisals
of the classroom disruption during teaching, we, first of all, have to
conclude that our hypotheses were not supported, as neither confidence
appraisal nor disruptiveness appraisal showed any notable correlations
with teachers' means standardized HR or any explanatory power over and
beyond teaching experience. Possibly, teachers' self-reported
appraisals, and their actual physiological stress responses, tap into
quite different phenomena, or at least, quite different aspects of the
multifaceted stress response \citep{kyriacou1978}. In addition, while HR
was assessed online during teaching, self-reported appraisals were given
in retrospect during the SRI, and may be subject to biased (e.g.,
self-serving) reporting or simply an inability to recall one´s immediate
stress reactions.

@@

@@

This study investigated whether HR data collected from teacher-worn
fitness trackers are suitable for exploring links between HR, subjective
stressor appraisal, and individual teaching experience, to achieve a
more profound comprehension of teacher stress. Results suggest that the
widespread availability of HR data from wearable fitness trackers,
moving ``from heartbeat to data'', presents opportunities both to
teachers for self-monitoring stress levels, and to researchers for
assessing physiological indicators of stress. For example, using fitness
trackers could enable teachers to strengthen their self-awareness in
stressful situations and allow for early self-intervention such as
mindfulness techniques (e.g., deep breathing or body scans)
\citep{agyapong2023interventions}. Integrating fitness trackers into
teacher training and everyday practice could offer an affordable and
practical method for assessing and managing teacher stress. In teacher
training as well as in research, triangulating data from fitness
trackers, lesson videos, and interviews could provide teachers with
insights into their own stress management, and foster the implementation
of effective stress and classroom management strategies. Taken together,
our findings cater to \citet{wettstein2021} call for the use of
ambulatory assessment methods, particularly in the context of classroom
disruptions, for gaining a deeper understanding of teacher stress and
its impact on both psychological and physiological variables.

@@

\begin{table}[ht]
    \centering
    \caption{\\
    Classification of nine, typical classroom disruptions according to \cite{lohmann2003schulern} performed in the micro-teaching unit by actors.}
    \begin{tabularx}{\textwidth}{XXX}
        \toprule
        \textbf{Verbal disruptions} & \textbf{Physical disruptions} & \textbf{Lack of eagerness to learn} \\
        \midrule
        Heckling & Clicking pen & Looking at phone \\
        Chatting & Snipping hands & Drawing \\
        Whispering & Drumming hands & Head on table \\
        \bottomrule
    \end{tabularx}
    \label{tab.a1}
\end{table}

\begin{figure}[htbp]
  \centering
  \caption{\\
  Laboratory setting of the micro-teaching unit. Note. The setting included three actors as the class (left) and a teacher (participant, right).}
  \includegraphics[width=0.5\textwidth]{appendix_figure1.png}
  \label{fig.a1}
\end{figure}

\begin{figure}[htbp]
  \centering\caption{\\
  Laboratory setting of the interview. Note. The experimenter and participant watched the previously taught micro-teaching unit on video.}
  \includegraphics[width=0.5\textwidth]{appendix_figure2.png}
  \label{fig.a2}
\end{figure}

>>>>

  \title{From heartbeat to data -- Using wearable fitness trackers as an
affordable approach to assess teacher stress}
    \author[Leipzig University]{Mandy Klatt%
  \corref{cor1}%
  \fnref{1}}
   \ead{mandy.klatt@uni-leipzig.de} 
    \author[University of Greifswald]{Peer Keßler%
  %
  \fnref{2}}
   \ead{peer.kessler@uni-greifswald.de} 
    \author[Max Planck Institute for Evolutionary Anthropology]{Gregor
Kachel%
  %
  \fnref{3}}
   \ead{gregor@example.com} 
    \author[Leipzig University]{Christin Lotz%
  %
  \fnref{4}}
   \ead{christin.lotz@uni-leipzig.de} 
    \author[Leipzig University]{Anne Deiglmayr%
  %
  \fnref{5}}
   \ead{anne.deiglmayr@uni-leipzig.de} 
      \affiliation[Leipzig University]{
    organization={Empirische Schul- und
Unterrichtsforschung},addressline={Marschnerstr.
29},city={Leipzig},postcode={4109},state={Sachsen},country={Germany},}
    \affiliation[Max Planck Institute for Evolutionary Anthropology]{
    organization={Department},addressline={Deutscher Pl.
6},city={Leipzig},postcode={4103},state={Sachsen},country={Germany},}
    \affiliation[University of Greifswald]{
    organization={Institute of Psychology},addressline={Robert-Blum-Str.
13},city={Greifswald},postcode={17489},state={Mecklenburg-Vorpommern},}
    \cortext[cor1]{Corresponding author}
    \fntext[1]{Conceptualization, Methodology, Formal analysis,
Investigation, Data Curation, Writing - Original Draft}
    \fntext[2]{Conceptualization, Methodology, Writing - Review \&
Editing, Supervision}
    \fntext[3]{Formal analysis, Data Curation, Writing - Review \&
Editing}
    \fntext[4]{Conceptualization, Methodology, Writing - Review \&
Editing}
    \fntext[5]{Conzeptualization, Methodology, Writing - Review \&
Editing, Supervision}

@@

Each participant came to the lab for a period of approximately two hours
in total, and each participant underwent the same phases (see Figure
\ref{fig.2}): In the \emph{pre-teaching phase}, the experimenter
welcomed the participants and helped them put on the fitness tracker.
This was followed by a warm-up session to familiarize the participants
with the laboratory setting and the class. This phase took about 10-15
minutes and participants spent this time mostly standing or slowly
walking around. During the \emph{teaching phase}, the participants held
their self-prepared micro-teaching unit to a class of three trained
actors who performed nine, potentially disruptive, classroom events
(e.g., chatting with a neighbor, heckling, looking at the phone; see
Table \ref{tab_a1} in the supplementary material for an overview and
categorization of all events; and Figure \ref{fig.a2} in the
supplementary material for a depiction of the laboratory setting of the
micro-teaching unit). The topic and class level of the teaching unit
could be freely chosen by the teachers with the only requirement that
the unit had to be an introductory lesson, and had to consist of
supervised individual work and / or frontal teaching. The micro-teaching
unit lasted about 15-20 minutes. Participants spent this time mostly
standing or slowly walking around. While teaching, participants wore
eye-tracking glasses, and their lesson was video-recorded. After having
completed the micro-teaching unit, in the \emph{post-teaching phase},
participants filled in questionnaires for approximately 10-15 minutes: a
brief computer-based survey of sociodemographic

@@

Since we aimed to keep measurement intervals comparable between study
phases, we aggregated HR over a representative 10-minute interval within
each phase (cf.~Figure \ref{fig.2}). Previous research has indicated
that 10-minute intervals are a useful duration for analyzing PPG data
\citep{lu2008can}. The intervals were selected based on the following
rules: The \emph{pre-teaching interval} (\(I_1\)) comprised the first 10
minutes after the fitness tracker had been put on. The \emph{teaching
interval} (\(I_2\)) started two minutes after the lesson had started.
This interval was of the highest relevance to our study. We explicitly
chose an early 10-minute interval within the teaching phase, as previous
studies revealed that the beginning of a lesson is most demanding and
potentially stressful with regards to teacher-student interaction
\citep{donker2018, claessens2017positive}. The \emph{post-teaching
interval} (\(I_3\)) started immediately after the end of the teaching
unit. The \emph{interview interval} (\(I_4\)) was defined as the mid-10
minutes between the end of the teaching unit and the time point when the
fitness tracker was taken off. All participants were being interviewed
during this interval. The end interval (\(I_5\)) comprised the last 10
minutes before the fitness tracker was taken off.

@@

To enable visual inspection of HR trends, we displayed smoothed teacher
HR over the course of the recording.\footnote{The curve was smoothed
  using the geom\_smooth() function from the ggplot2 package in R
  \citep{ggplot2} based on the smoothing method LOESS (Locally Estimated
  Scatterplot Smoothing). This method fits a polynomial surface
  determined by one or more numerical predictors, using local fitting.}
We visually compared unstandardized and standardized HR trends over the
two-hour recording period.\footnote{Note that the study exceeded the
  planned duration of two hours for a few participants. To avoid
  distortions when mapping the HR over the course of the study (see
  Figure \ref{fig.3}), the endpoint was set at two hours for all
  participants, even though data from later time points was used in the
  \emph{end interval} for a few participants.} For all further analyses,
we used standardized rather than unstandardized HR values.

@@

Addressing our second research goal, we ran linear regression analysis
with teaching experience and subjective appraisals as predictors. To
test Hypothesis 2a, we examined the effect of teaching experience on
participants' HR levels (i.e., mean standardized HR) for each of the
five intervals, using linear regression models with teaching experience
as the sole predictor. To test Hypotheses 2b and 2c, we separately
augmented the model by either teachers' disruption appraisal (Hypothesis
2b) or confidence appraisal (Hypothesis 2c) as predictors, while
controlling for teaching experience. To test Hypothesis 2d, we examined
the effects of all three predictors in one regression model.
Furthermore, we repeated these steps to explore the effects of teaching
experience and subjective appraisals on \emph{changes} in teachers' HR
(i.e., mean slopes).\footnote{Please note: HR levels and changes were
  not regressed on the disruption and confidence appraisals in the
  \emph{pre-teaching interval} (\(I_1\)), because the appraised
  classroom events had not yet taken place in that phase.}

@@

Table \ref{tab_3} shows the raw correlations among mean standardized
HR/mean slopes (see Table \ref{tab_2} for means and standard
deviations), teaching experience (\(M = 5.64\), \(SD = 9.46\)),
disruption appraisal (\(M = 5.19\), \(SD = 2.87\)), and confidence
appraisal (\(M = 7.81\), \(SD = 1.97\)). With a few notable exceptions,
correlations with HR measures were mostly very small and statistically
non-significant (Table 3). Correlations between teaching experience and
appraisals (not shown in Table \ref{tab_3}) were substantial: more
experienced teachers gave lower disruption appraisals (\(r = -.36\)),
and higher confidence appraisals (\(r = .44\)). Moreover, the two
appraisal variables were negatively correlated (\(r = -.37\)).

Table \ref{tab_4} shows the results of the regression analyses. Teaching
experience significantly predicted mean standardized HR only in the
\emph{interview interval} (Table \ref{tab_4}, \emph{interview interval},
Model 1), indicating a higher mean standardized HR for teachers with
more teaching experience. This relationship is, in fact, in the opposite
direction as predicted by Hypothesis 2a. Neither adding disruption
appraisal (Hypothesis 2b) nor adding confidence appraisal (Hypothesis
2c) increased the amount of explained variance to a statistically
significant extent.

When considering the effects of the three predictors in concert
(Hypothesis 2d), mean standardized HR was significantly predicted only
by disruption appraisal, and only in the \emph{post-teaching interval}
(Table \ref{tab_4}, \emph{post-teaching interval}, Model 4), indicating
a higher mean standardized HR for teachers who felt more disrupted by
the classroom events, when controlling for the other variables.

@@

Building on the model of teacher stress \citep[see Fig.
2]{kyriacou1978}, we had hypothesized that more experienced teachers,
with better classroom management skills at their disposal, experience
less physiological stress when dealing with classroom disruptions.
Contrary to our expectations, we found no buffering effect of teaching
experience on teachers' HR, i.e., more experienced teachers did not show
lower mean standardized HR during the stressful teaching phase than less
experienced teachers. Rather, at least descriptively, we observed the
opposite trend. There are several possible explanations for this
finding. First, teaching experience is inherently confounded with age
(the two variables correlated at \(r = .94\) in our sample), and age has
been shown to affect indicators of cardiovascular reactivity in various
ways \citep{uchino2010older}. However, to avoid this kind of confounding
influence, we had used not raw BPM but rather standardized mean HR for
all our analyses, thus controlling at least for inter-individual
differences in mean HR. Second, as research on teacher
professionalization has repeatedly shown, professional experience is not
a guarantee for higher professional knowledge and skills
\citep{kirschner2016professionswissen}. Rather, honing skills from
professional experience necessitates a deliberate practice of choosing
to improve, learning through experience, and integrating new knowledge
into future performances \citep{dunn1999deliberate}. Thus, rather than
professional experience alone, more direct assessments of classroom
management skills, such as objective behavior-based tests, would be a
better indicator of expertise that future studies could explore.

@@

\noindent Finally, and most importantly, the highly controlled teaching
situation that we created in the lab might not have provided sufficient
resemblance to the expert teachers' working conditions to let them
effectively use their coping resources. In other words, since the
situation was unfamiliar to both experienced and unexperienced teachers,
their stress levels might have been more similar than they would have
been in a more authentic classroom setting.

While we did not find a buffering effect of teaching experience on mean
HR during teaching, we did, however, find a less steep HR increase in
more experienced, compared to less experienced teachers during the
\emph{pre-teaching phase} (\(\beta = -.27\)), i.e., in preparation for
the micro-teaching unit. This finding supports the idea that, even
though teaching experience guarantees neither superior expertise nor
stress resistance, the habits and routines formed by experienced
teachers may at least lead to lower arousal levels (e.g., experienced as
feeling less nervous and tense) when they anticipate potentially
stressful teaching situations.

An interesting observation beyond our hypotheses was that teaching
experience was predictive of HR differences, not during teaching, but in
the \emph{interview phase}: compared to less experienced teachers, more
experienced teachers showed a higher mean standardized HR
(\(\beta = .24\)) and, thus, probably experienced higher levels of
physiological stress during the SRI. One possible explanation for this
finding could again be the higher age of the more experienced teachers,
along with slower recovery from stress in older teachers. For instance,
\citet{ritvanen2006responses} observed that, compared to their younger
colleagues, older teachers did not experience a decrease in their HR
during periods of low stress levels, from which they concluded that
recovery from stress was insufficient in the older teachers
\citep{ritvanen2006responses}. Alternatively, the finding could also be
attributed to the fact that less experienced teachers, due to their
ongoing or only recently concluded training, may have been more
accustomed to reflecting on their work and receiving feedback as was the
case during the SRI, whereas, these activities were less routine and
possibly more face-threatening for experienced teachers. Therefore, it
is possible that more experienced teachers found the interview itself to
be more stressful and therefore showed a higher mean standardized HR
during this phase.

With regards to the predictive power of teachers' subjective appraisals
of the classroom disruption during teaching, we, first of all, have to
conclude that our hypotheses were not supported, as neither confidence
appraisal nor disruptiveness appraisal showed any notable correlations
with teachers' mean standardized HR or any explanatory power over and
beyond teaching experience. Possibly, teachers' self-reported
appraisals, and their actual physiological stress responses, tap into
quite different phenomena, or at least, quite different aspects of the
multifaceted stress response \citep{kyriacou1978}. In addition, while HR
was assessed online during teaching, self-reported appraisals were given
in retrospect during the SRI, and may be subject to biased (e.g.,
self-serving) reporting or simply an inability to recall ones immediate
stress reactions.

@@

This study investigated whether HR data collected from teacher-worn
fitness trackers are suitable for exploring links between HR, subjective
stressor appraisal, and individual teaching experience, to achieve a
more profound comprehension of teacher stress. Results suggest that the
widespread availability of HR data from wearable fitness trackers,
moving ``from heartbeat to data'', presents opportunities both to
teachers for self-monitoring stress levels, and to researchers for
assessing physiological indicators of stress. For example, using fitness
trackers could enable teachers to strengthen their self-awareness in
stressful situations and allow for early self-intervention such as
mindfulness techniques (e.g., deep breathing or body scans;
\citet{agyapong2023interventions}). Integrating fitness trackers into
teacher training and everyday practice could offer an affordable and
practical method for assessing and managing teacher stress. In teacher
training as well as in research, triangulating data from fitness
trackers, lesson videos, and interviews could provide teachers with
insights into their own stress management, and foster the implementation
of effective stress and classroom management strategies. Taken together,
our findings cater to \citet{wettstein2021} call for the use of
ambulatory assessment methods, particularly in the context of classroom
disruptions, for gaining a deeper understanding of teacher stress and
its impact on both psychological and physiological variables.

@@

\begin{table}[ht]
    \centering
    \caption{\\
    Classification of nine, typical classroom disruptions according to \cite{lohmann2003schulern} performed in the micro-teaching unit by actors.}
    \begin{tabularx}{\textwidth}{XXX}
        \toprule
        Verbal disruptions & Physical disruptions & Lack of eagerness to learn \\
        \midrule
        Heckling & Clicking pen & Looking at phone \\
        Chatting & Snipping hands & Drawing \\
        Whispering & Drumming hands & Head on table \\
        \bottomrule
    \end{tabularx}
    \label{tab_a1}
\end{table}

\begin{figure}[htbp]
  \centering
  \caption{\\
  Laboratory setting of the micro-teaching unit. .}
  \includegraphics[width=0.5\textwidth]{appendix_figure1.png}
  \caption*{\textit{Note.} The setting included three actors as the class (left) and a teacher (participant, right).}
  \label{fig.a1}
\end{figure}

\begin{figure}[htbp]
  \centering\caption{\\
  Laboratory setting of the interview.}
  \includegraphics[width=0.5\textwidth]{appendix_figure2.png}
  \caption*{\textit{Note.} The experimenter and participant watched the previously taught micro-teaching unit on video.}
  \label{fig.a2}
\end{figure}
